
```{r}
source(here::here("R/load.R"))
```

```{r}
dir_info("../images/sample-photos-tidy") %>% 
    transmute(
        path = str_remove_all(path, "^\\.\\./")
    ) %>% 
    mutate(
        output = glue("output/sample-photos-tidy-frame/{basename(path)}")
    ) %>% 
    transmute(
        text = 
            glue("python face_detect_demo.py --img={path} --output={output}")
    ) %>% 
    summarise(
        str_flatten(text, "\n")
    ) %>% 
    pull %>% 
    clipr::write_clip()
```


python face_detect_demo.py --img=images/sample-photos-tidy/022_3.bmp --output=output/sample-photos-tidy-frame/022_3.bmp
python face_detect_demo.py --img=images/sample-photos-tidy/143_3.bmp --output=output/sample-photos-tidy-frame/143_3.bmp
python face_detect_demo.py --img=images/sample-photos-tidy/204_1.bmp --output=output/sample-photos-tidy-frame/204_1.bmp
python face_detect_demo.py --img=images/sample-photos-tidy/227_2.bmp --output=output/sample-photos-tidy-frame/227_2.bmp
python face_detect_demo.py --img=images/sample-photos-tidy/263_2.bmp --output=output/sample-photos-tidy-frame/263_2.bmp
python face_detect_demo.py --img=images/sample-photos-tidy/274_4.bmp --output=output/sample-photos-tidy-frame/274_4.bmp
python face_detect_demo.py --img=images/sample-photos-tidy/393_4.bmp --output=output/sample-photos-tidy-frame/393_4.bmp
python face_detect_demo.py --img=images/sample-photos-tidy/440_4.bmp --output=output/sample-photos-tidy-frame/440_4.bmp
python face_detect_demo.py --img=images/sample-photos-tidy/444_4.bmp --output=output/sample-photos-tidy-frame/444_4.bmp
python face_detect_demo.py --img=images/sample-photos-tidy/469_2.bmp --output=output/sample-photos-tidy-frame/469_2.bmp

```{r}
dir_info("../output/sample-photos-tidy-frame/") %>% 
    summarise(
        time_diff = max(birth_time) - min(birth_time),
        n = n()
    ) %>% 
    mutate(
        avg = time_diff/n
    )
```

